---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%",
  asciicast_at = "all",
  asciicast_theme = "readme"
)
asciicast::init_knitr_engine()
```

# askgpt

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
<!-- badges: end -->

The goal of askgpt is to help you to learn R, using a ChatGPT-like prompt and answer system.
It sends prompts to [openai's API](https://openai.com/api/) directly from R.
It also has some additional functionality:

- Prompt "What is wrong with my last command?" (or "help!") to get help on the last error R emmitted
- Prompt "Can you elaborate on that?" (or "what?") to ask GPT to elaborate on the last reply
- Use the RStudio addin to comment, annotate or explain highlighted code

## Installation

You can install the development version of askgpt like so:

``` r
remotes::install_github("JBGruber/askgpt")
```

Then you should get a key for the openai API on [this page](https://openai.com/api/).
Save it to your project with:

```{r eval=FALSE}
usethis::edit_r_environ(scope = "project")
```

In the format:

```{r eval=FALSE}
OPENAI_API_KEY = "xxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxx"
```


## Demo

```{asciicast, cache = TRUE}
library(askgpt)
log_init()
askgpt("What is an R function?")

askgpt("Can you help me with the function aes() from ggplot2?")

# this is a special trigger prompt that sends your last command to GPT
mean[1]
askgpt("What is wrong with my last command?") 

# the api does not really have a memory, the last prompt is sent to the API again
askgpt("Can you elaborate on that?") 
```


