---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%",
  eval = FALSE
)
```

# askgpt

<!-- badges: start -->
<!-- badges: end -->

The goal of askgpt is to help you to learn R using a ChatGPT-like prompt and answer system.
It wraps the [openai](https://github.com/irudnyts/openai/) package and let's you ask question from the R Console directly.

## Installation

You can install the development version of askgpt like so:

``` r
remotes::install_github("JBGruber/askgpt")
```

Then you should get a key for theopenai API on [this page](https://openai.com/api/).
Save it to your project with:

```{r}
usethis::edit_r_environ(scope = "project")
```

In the format:

```{r}
OPENAI_API_KEY = "xxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxx"
```


## Example

![video of examples](man/figures/askgpt.webm)

```{r example}
library(askgpt)
library(askgpt)
log_init() # run to enable error logging
askgpt("What is an R function?")
mean[1]
askgpt("What is wrong with my last command?") # this is a special trigger prompt that sends your last command to GPT
askgpt("Can you help me with the function aes() from ggplot2?")
askgpt("Can you elaborate on that?") # the api does not really have a memory, the last prompt is sent to the API again
```


