---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# askgpt

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
<!-- badges: end -->

The goal of askgpt is to help you to learn R, using a ChatGPT-like prompt and answer system.
It sends prompts to [openai's API](https://openai.com/api/) directly from R.
It also has some additional functionality:

- Prompt "What is wrong with my last command?" (or "help!") to get help on the last error R emmitted
- Prompt "Can you elaborate on that?" (or "what?") to ask GPT to elaborate on the last reply
- Use the RStudio addin to comment, annotate or explain highlighted code

See more under 

## Installation

You can install the development version of askgpt like so:

``` r
remotes::install_github("JBGruber/askgpt")
```

```{r echo=FALSE, results='asis'}
fig_path = "vignettes/figs"
res <- knitr::knit_child("vignettes/Usage.Rmd", quiet = TRUE)
cat(res, sep = '\n')
```

